---
title: "Exercise 2"
author: "Dr Jamie Owen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{exercise3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Model Assessment

1. `mtcars` is a data set of information on cars that is distributed with R. You can access it by typing its name

```{r}
head(mtcars)
```

2. For penalised regression we need to scale predictors. In this example we want to predict `mpg`, the efficiency of each car. The code below will separate the response from the predictors and scale the predictors to have 0 mean, unit variance. 

```{r}
y_train = mtcars[,1]
x_train = mtcars[,-1]
x_scaled = scale(x_train)
```


3. Fit a lasso model to this data. 

```{r,message = FALSE}
library(glmnet)
fit = glmnet(x_scaled,y_train, alpha = 1)
```


4. Use `cv.glmnet` to find a good choice of penalty for the lasso model

```{r, echo = FALSE}
fit_cv = cv.glmnet(x_scaled,y_train,alpha = 1)
```


5. You can extract coefficents from the object returned in question 4 with (in my case I stored the result of cross validation in `fit_cv`). How do these compare to standard linear regression?

```{r,eval = FALSE}
coef(fit_cv, s = "lambda.min")
```

